\documentclass[11pt,english, answers]{exam}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\listfiles

\usepackage{fullpage}
\usepackage[showframe=false,margin=1in]{geometry}
\parindent=0pt
\usepackage{relsize}
\usepackage[T1]{fontenc} % for properly hyphenating words with accented chars
\usepackage[latin1]{inputenc}
\usepackage{babel}

% figure management
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subfig}
\usepackage[belowskip=0pt,aboveskip=0pt,font=small]{caption}
\setlength{\intextsep}{7pt plus 0pt minus 0pt}
\usepackage{tikz}

% math
\usepackage{amsmath, amsthm, amssymb}

%\usepackage{amstext}
\usepackage{textcomp}
\usepackage{stmaryrd}
\usepackage{upgreek}
\usepackage{bm}
\usepackage{cases}

% code
\usepackage{listings}

% assorted
\usepackage{url}
\usepackage{breakurl}
\usepackage[colorlinks=true]{hyperref}
\usepackage{xspace}
\usepackage{comment}
\usepackage{color}
\usepackage{afterpage}
\usepackage[normalem]{ulem}
\usepackage{enumitem}
\usepackage{xparse}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Shortcuts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{assets/mysymbols}
\input{assets/math_definition.tex}
\newcommand{\hide}[1]{}
\newcommand{\x}{\mathbf{x}}
\newcommand{\wb}{\mathbf{w}}
\lstset{language=C,keywordstyle={\bfseries \color{blue}}}
\NewDocumentCommand{\codeword}{v}{%
	\texttt{\textcolor{blue}{#1}}%
}

\checkedchar{\tikz\draw[black,fill=black] (0,0) circle (1.0ex);}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title / Author
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{CS 4644/7643: Deep Learning\\
Spring 2022 \\
Problem Set 0}
\author{Instructor: Zsolt Kira \\
TAs: Bhavika Devnani, Jordan Rodrigues, Mandy Xie, \\Yanzhe Zhang, Amogh Dabholkar, Ahmed Shaikh, \\ Ting-Yu Lan, Anshul Ahluwalia, Aditya Singh \\
Discussions: \url{https://piazza.com/gatech/spring2022/cs46447643a}}
\date{Due: Thursday, Jan 13, 11:59pm ET}

\maketitle

\paragraph*{Instructions}
\begin{enumerate}
 \item We will be using Gradescope to collect your assignments.  Please read the following instructions for submitting to Gradescope carefully! Failure to follow these instructions may result in parts of your assignment not being graded. We will not entertain regrading requests for failure to follow instructions.
      \begin{itemize}
        \item
          For Section 1: Multiple Choice Questions, it is mandatory to use the {\LaTeX} template provided on the class webpage (\url{https://www.cc.gatech.edu/classes/AY2022/cs7643_spring/assets/ps0.zip}).
           For every question, there is only one correct answer. To mark the correct answer, change \codeword{\choice} to \codeword{\CorrectChoice}

           \item
                For Section 2: Proofs - This section has 7 total problems/sub-problems (Q8, Q9a - Q9c and Q10a - Q10c) and your answer to each sub-problem should start on a new page. Please be sure to mark the corresponding pages to the correct question numbers marked on the PS0 outline while submitting on Gradescope. 
           \item For Section 2, \LaTeX'd  solutions are strongly encouraged (solution template
           available at \\
           \url{https://www.cc.gatech.edu/classes/AY2022/cs7643_spring/assets/ps0.zip}),
           but scanned handwritten copies are acceptable. If you scan handwritten copies, please make sure to append them to the PDF generated by {\LaTeX} for Section 1 and please mark the pages correctly as mentioned above. 

      \end{itemize}

 \item Hard copies are \textbf{not} accepted.
\item We generally encourage you to collaborate with other students. You may talk to a friend,
discuss the questions and potential directions for solving them. However, you need to write
your own solutions and code separately, and \emph{not} as a group activity.
Please list the students you collaborated with. \\
\textbf{Exception: PS0 is meant to serve as a background preparation test. You must NOT collaborate on PS0.}

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Body
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
\input{mcq}
\input{proofs}
%input{prob}
%\input{calculus}
%\input{softmax}

\end{document}
