For this homework's paper review section, we turn to the interesting and increasingly important field of Explainable AI. 

\vspace{2mm}

The following paper \textbf{Multimodal Explanations: Justifying Decisions and Pointing to the Evidence}, which was presented at CVPR 2018, introduces a unique multi-modal approach to explainability by joint textual rationale generation and attention visualization - in the tasks of visual question answering (VQA) and activity recognition. This was a major improvement over pre-existing unimodal explainability techniques (such as the ones covered in the coding section of HW3), with the results showing complementary explanatory strengths from the visual and textual explanations. 

\vspace{2mm}

The paper can be viewed \href{https://openaccess.thecvf.com/content_cvpr_2018/html/Park_Multimodal_Explanations_Justifying_CVPR_2018_paper.html}{here}.
\vspace{2mm}
The evaluation rubric for this section is as follows:
\begin{enumerate}[resume]
\item
\textbf{[2 points]}
Briefly summarize the key contributions, strengths and weaknesses of this paper.

\item
\textbf{[2 points]}
What is your personal takeaway from this paper? This could be expressed either in terms of relating the approaches adopted in this paper to your traditional understanding of explainability techniques, or potential future directions of research in the area which the authors haven't addressed, or anything else that struck you as being noteworthy. 

\end{enumerate}

Guidelines: Please restrict your reviews to at least one paragraph per question, but no more than 350 words (total length for answers to both of the above questions). Please write separate answers for each question to assist in Gradescope grading.