\documentclass[11pt,english]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Package imports are stored in /assets/base-packages.tex
% Packages specific to this pset can be imported here.

\listfiles
\input{assets/base-packages.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Shortcuts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{assets/mysymbols}
\input{assets/math_definition.tex}
\renewcommand{\hide}[1]{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title / Author
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{CS4803-7643: Deep Learning\\
Spring 2022 \\
Problem Set 4}

% NOTE: Any changes to instructor, TAs, or piazza link should be done in the file below
\input{assets/instructor-and-TAs}
\date{Due: Monday, April 4, 11:59pm}
\maketitle



\paragraph*{Instructions}
\begin{enumerate}
\item We will be using Gradescope to collect your assignments.  Please read the following instructions for submitting to Gradescope carefully!
     \begin{itemize}
          \item 
                For the \textbf{HW4 Writeup} component on Gradescope, please upload one single PDF containing the answers to all the theory questions, the report for the coding problems and the jupyter notebook \texttt{Machine\_Translation.ipynb} consisting of tests for parts of the code implementation. The solution to each problem/subproblem must be on a separate page. When submitting to Gradescope, please make sure to mark the page(s) corresponding to each problem/sub-problem.  
                Also, please make sure that your submission for the coding part only includes the files collected by the \texttt{collect\_submission} script, else the auto-grader will result in a zero, and we won't accept regrade requests for this scenario given the size of the class.
                Likewise, the pages of the report must also be marked to their corresponding subproblems. 

          \item
               For the coding problem, please use the provided \texttt{collect\_submission.py} script and
               upload the resulting file to the \textbf{HW4 Code} assignment on Gradescope. While we will
               not be explicitly grading your code, you are still required to submit it. Please make sure
               you have saved the most recent version of your code before running this
               script.

          \item
               Note: This is a large class and Gradescope's assignment segmentation features are essential.
               Failure to follow these instructions may result in parts of your assignment not being graded.
               We will not entertain regrading requests for failure to follow instructions.


               Please read \url{https://stats200.stanford.edu/gradescope_tips.pdf} for additional information on submitting to Gradescope.
     \end{itemize}

\item
    \LaTeX'd  solutions are strongly encouraged (solution template
     available on Canvas---Assignment 4 HW),
     but scanned handwritten copies are acceptable.
     Hard copies are \textbf{not} accepted.


\item We generally encourage you to collaborate with other students.

You may talk to a friend,
discuss the questions and potential directions for solving them. However, you need to write
your own solutions and code separately, and \emph{not} as a group activity.
Please list the students you collaborated with. \\ \\

\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Body
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Collaborators [0.5 points]}

\input{question-bank/Misc/collaborators}


\section{Recurrent Neural Networks and Transformers}
\begin{enumerate}[start]

\item
\textbf{[Vanilla RNN for parity function: 3 points]}
\input{question-bank/RNNs/vanilla-RNN_parity}

\item
\textbf{[LSTM for parity function: 5 points]}
\input{question-bank/RNNs/LSTM-parity}

\item
\textbf{[When to Stop in Beam Search: 5 points]}
\input{question-bank/Misc/beam-search}

\item
\textbf{[Exploding Gradients: 5 points]}
\input{question-bank/Theory/exploding-gradients}

\item
\textbf{[Transformer as GNN: 5 points; Extra credit for both 4803 and 7643]}
\input{question-bank/RNNs/transformer-as-GNN}

\end{enumerate}

\section{Paper Review [Extra credit for 4803, regular credit for 7643]}

% Point values for paper review defined in the question file
\input{question-bank/Paper_Reviews/multimodal-explanations}

\section{Coding: Machine Translation with Seq2Seq and Transformers}

\textbf{[20 points]}
\input{question-bank/Coding/image-captioning}

Points breakdown:
\begin{itemize}
    \item HW4 Code
    \begin{itemize}
        \item Autograder [11 points]
    \end{itemize}
    \item HW4 Writeup
    \begin{itemize}
        \item Theory Answers [18 points for 4803/ 22 points for 7643]
        \item Report PDF [9 points]
        \begin{itemize}
            \item Description and results for Seq2Seq [4 points]
            \item Description and results for Transformer [5 points]
        \end{itemize}
        \item Jupyter Notebook as PDF
    \end{itemize}
\end{itemize}

\end{document}
